---
title: "Bayes Methods"
author: "Bryana A.S. Thieret"
format: pdf
---


```{r warning=FALSE, output=FALSE}
library(tidyverse)
library(readxl)
library(R2WinBUGS)
```


```{r warning=FALSE, output=FALSE}
C2015 = tibble::tibble(
  "Week" = c(1, 2, 3, 4, 5, 6, 1, 2, 3, 4, 5, 6, 1, 2, 3, 4, 5, 6),
  "Group" = c("AFR", "AFR", "AFR", "AFR", "AFR", "AFR", "MS15", "MS15", "MS15", "MS15", "MS15", "MS15", "MS360", "MS360", "MS360", "MS360", "MS360", "MS360"),
  "Ethanol_Percentage" = c(5, 5, 20, 20, 20, 20, 5, 5, 20, 20, 20, 20, 5, 5, 20, 20, 20, 20),
  "Access_Hours" = c(24, 2, 2, 2, 2, 2, 24, 2, 2, 2, 2, 2, 24, 2, 2, 2, 2, 2),
  "Median" = c(1.61, 0.40, 1.10, 1.21, 1.37, 1.18, 1.89, 0.67, 1.12, 1.49, 1.23, 1.32, 1.53, 0.57, 1.20, 1.11, 1.28, 1.32),
  "a" = c(0.29, 0.18, 0.50, 0.59, 0.77, 0.62, 0.87, 0.32, 0.75, 0.89, 1.05, 0.39, 0.21, 0.09, 0.29, 0.56, 0.38, 0.60),
  "b" = c(4.16, 0.75, 2.11, 1.42, 2.08, 1.66, 3.40, 0.99, 1.61, 2.13, 1.74, 1.77, 3.28, 1.14, 1.98, 2.15, 2.52, 2.05),
  "n" = c(11, 11, 11, 11, 11, 11, 10, 10, 10, 10, 10, 10, 20, 20, 20, 20, 20, 20),
  "Sessions" = c(3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3))
C2015 = C2015 |>
  mutate(
    Estimated_Mean = (a+2*Median+b)/(4),
    Estimated_SD = ((b - a)/(2 * qnorm((n-0.375)/(n+0.25)))),
    Estimated_Variance = (Estimated_SD)^2
  )


C2015 |> filter(Group != "AFR") |> mutate(article = "C2015") |> mutate(Group = factor(Group)) |> select(article, Week, Group, Ethanol_Percentage, Estimated_Mean, Estimated_Variance, n)

control = C2015 |> filter(Group != "AFR") |> slice(1:6) |> select(Week, n, Estimated_Mean, Estimated_SD) |> rename("Estimated_Mean_2" = Estimated_Mean,
                                                                                           "n_2" = n, "Estimated_SD_2" = Estimated_SD)
ms = C2015 |> filter(Group != "AFR") |> slice(7:12) |> select(Week, n, Estimated_Mean, Estimated_SD) |> rename("Estimated_Mean_1" = Estimated_Mean,
                                                                                           "n_1" = n, "Estimated_SD_1" = Estimated_SD)

C15 = left_join(ms, control) |> 
  mutate(article = "C2015") |> 
  mutate(mean_diff = Estimated_Mean_1 - Estimated_Mean_2,
         pooled_SD = sqrt(((n_1 - 1)*Estimated_SD_1^2 + (n_2 - 1)*Estimated_SD_2^2) / (n_1+n_2 - 2)),
         sd_diff = Estimated_SD_1 - Estimated_SD_2, 
         yij = mean_diff/pooled_SD) |> select(article, Week, mean_diff, pooled_SD, yij, sd_diff) |>
  rename("timepoint" = Week)
```


```{r warning=FALSE, output=FALSE}

GN2006 <- read_excel("G&N2006.xlsx")
GN2006 = GN2006 |> group_by(Phase, Group) |> summarise(mean = mean(Ethanol_Intake),
                                              sd = sd(Ethanol_Intake),
                                              variance = var(Ethanol_Intake), 
                                              n = n()) 

control = GN2006 |> filter(Group == "MS15") |> rename("mean_2" = mean,
                                            "sd_2" = sd, "n_2" = n) |> 
  select(-variance, -Group)

ms = GN2006 |> filter(Group == "MS360") |> rename("mean_1" = mean,
                                            "sd_1" = sd, "n_1" = n) |> 
  select(-variance, -Group)

GN06 = left_join(ms, control, by = "Phase") |>
  mutate(article = "GN2006") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2,
         yij = mean_diff/pooled_SD) |>
  mutate(timepoint = case_when(
    Phase == "Acquisition" ~ 2,
    Phase == "Maintenance" ~ 4,
    Phase == "Stabilization" ~ 6
  )) |> select(article, mean_diff, pooled_SD, yij, timepoint, sd_diff)

```


```{r warning=FALSE, output=FALSE}
P2003 <- read_excel("P2003.xlsx")

Sessions = tibble::tibble(Ethanol_Percentage = c(2, 4, 6, 8),
               Sessions = c(4, 4, 7, 11),
               n = c(8, 8, 8, 8))

P2003 = left_join(P2003, Sessions, by = "Ethanol_Percentage")

P2003 = P2003 |> mutate(SD = SEM*sqrt(n),
                        variance = SD^2)

control = P2003 |> filter(Group == "MS15") |> rename("mean_2" = Mean,
                                            "sd_2" = SD, "n_2" = n) |> 
  select(-variance, -Group, -Upper_Point, -SEM, -Sessions)

ms = P2003 |> filter(Group == "MS360") |> rename("mean_1" = Mean,
                                            "sd_1" = SD, "n_1" = n) |> 
  select(-variance, -Group, -Upper_Point, -SEM, -Sessions)

P03 = left_join(ms, control) |>
  mutate(article = "P2003") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2, 
         yij = mean_diff/pooled_SD) |> select(article, mean_diff, pooled_SD, yij, sd_diff) |>
  mutate(timepoint = c(1, 2, 3, 4))

```


```{r warning=FALSE, output=FALSE}
O2011 <- read_excel("O2011.xlsx")
O2011 = O2011 |> pivot_wider(names_from = Summary_Statistics, values_from = Values)

# estimated mean and SD from Wan et al., 2014
O2011 = O2011 |> mutate(
  Estimated_Mean = ((Minimum + 2*IQR1 + 2*Median + 2*IQR3 + Maximum)/8),
  Estimated_SD = (((Maximum - Minimum)/(4*qnorm((n-0.375)/(n+0.25)))) + ((IQR3-IQR1)/(4*qnorm((0.75*n-0.125)/(n+0.25))))),
  Estimated_Variance = (Estimated_SD)^2
) 

control = O2011 |> filter(Group == "MS15") |> rename("mean_2" = Estimated_Mean,
                                            "sd_2" = Estimated_SD, "n_2" = n) |> 
  select(-Estimated_Variance, -Group, -Sessions, -Maximum, -IQR3, -IQR1, -Ethanol_Percentage, -Minimum, -Median)

ms = O2011 |> filter(Group == "MS360") |> rename("mean_1" = Estimated_Mean,
                                            "sd_1" = Estimated_SD, "n_1" = n) |> 
  select(-Estimated_Variance, -Group, -Sessions, -Maximum, -IQR3, -IQR1, -Ethanol_Percentage, -Minimum, -Median) 
  
O11 = left_join(ms, control) |>
  mutate(article = "O2011") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2, 
         yij = mean_diff/pooled_SD) |> select(article, mean_diff, pooled_SD, yij, Week, sd_diff) |>
    rename("timepoint" = Week)
  
```


```{r warning=FALSE, output=FALSE}
G2007 <- read_excel("G2007.xlsx")
G2007 = G2007 |> group_by(Group, Days) |> summarise(Mean = mean(Mean_Ethanol_Intake),
                                            SD = sd(Mean_Ethanol_Intake), 
                                            Variance = var(Mean_Ethanol_Intake),
                                            n = n())

control = G2007 |> filter(Group == "MS15") |> rename("mean_2" = Mean,
                                            "sd_2" = SD, "n_2" = n) |> select(-Variance, -Group)
  
ms = G2007 |> filter(Group == "MS360") |> rename("mean_1" = Mean,
                                            "sd_1" = SD, "n_1" = n) |> select(-Variance, -Group)



G07 = left_join(ms, control, by = "Days") |>
  mutate(article = "G2007") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2, 
         yij = mean_diff/pooled_SD) |> select(article, mean_diff, pooled_SD, yij, Days, sd_diff) |>
    mutate(timepoint = case_when(
      Days == "1-18" ~ 2,
      Days == "19-36" ~ 4,
      Days == "37-54" ~ 6
    )) |> select(-Days)

```


```{r warning=FALSE, output=FALSE}
Daoura2011 = tibble::tibble(
  "Group" = c("MS0", "MS0", "MS0", "MS0", "MS0",
              "MS15", "MS15", "MS15", "MS15", "MS15",
              "MS360", "MS360", "MS360", "MS360", "MS360"),
  "Week" = c(1, 2, 3, 4, 5, 1, 2, 3, 4, 5, 1, 2, 3, 4, 5),
  "Median" = c(1.97, 1.71, 2.08, 2.58, 1.74, 
               1.64, 1.75, 1.73, 1.84, 1.83,
               1.69, 1.90, 1.62, 2.40, 2.72),
  "IQR" = c(1.14, 2.27, 1.83, 2.35, 1.79,
            1.11, 2.42, 1.59, 1.85, 1.49,
            0.58, 1.63, 2.36, 2.14, 1.67),
  "n" = c(15, 15, 15, 15, 15, 
          15, 15, 15, 15, 15,
          14, 14, 14, 14, 14)
)

Daoura2011 = Daoura2011 |> mutate(
  "IQR1" = Median - (IQR/2),
  "IQR3" = Median + (IQR/2)
)

# C3 method 
Daoura2011 = Daoura2011 |>
  mutate(
    Estimated_Mean = ((IQR1+Median+IQR3)/3),
    Estimated_SD = ((IQR3-IQR1)/(2*qnorm((0.75*n-0.125)/(n+0.25)))),
    Estimated_Variance = Estimated_SD^2
  )

control = Daoura2011 |> filter(Group == "MS15") |> rename("mean_2" = Estimated_Mean,
                                            "sd_2" = Estimated_SD, "n_2" = n) |> select(Week, n_2, mean_2, sd_2)

ms = Daoura2011 |> filter(Group == "MS360") |> rename("mean_1" = Estimated_Mean,
                                            "sd_1" = Estimated_SD, "n_1" = n) |> select(Week, n_1, mean_1, sd_1)


D11 = left_join(ms, control) |>
  mutate(article = "D11") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2, 
         yij = mean_diff/pooled_SD) |> select(article, Week, mean_diff, pooled_SD, yij, sd_diff) |>
  rename("timepoint" = Week)
```


```{r warning=FALSE, output=FALSE}
L2017 <- read_excel("L2017.xlsx") 

L2017 |> select(c(1:22)) |>
  pivot_longer(c(5:22), names_to = "Week", values_to = "Amount") |>
  mutate(Sessions = 3,
         Intake_Session = Amount/Sessions) |>
  group_by(Rearing, Supplier, Week) |>
  summarise(mean = mean(Intake_Session),
            sd = sd(Intake_Session))

diff_supplier = L2017 |> select(c(1:22)) |>
  pivot_longer(c(5:22), names_to = "Week", values_to = "Amount") |>
  mutate(Sessions = 3,
         Intake_Session = Amount/Sessions)

dif = lm(Intake_Session ~ Week*Supplier*Rearing, data = diff_supplier)
summary(dif) # no difference between suppliers and intake of ethanol (I can combine these)


L2017 = L2017 |> select(c(1:22)) |>
  pivot_longer(c(5:22), names_to = "Week", values_to = "Amount") |>
  filter(!is.na(Amount)) |>
  mutate(Sessions = 3,
         Intake_Session = Amount/Sessions) |>
  group_by(Rearing, Week) |>
  summarise(mean = mean(Intake_Session),
            sd = sd(Intake_Session),
            variance = var(Intake_Session))

control = L2017 |> filter(Rearing == "MS15") |> 
  slice(1:12) |> mutate(n = 10) |>
  rename("mean_2" = mean, "sd_2" = sd, "n_2" = n) |> select(Week, mean_2, sd_2, n_2)


ms = L2017 |> filter(Rearing == "MS360") |> 
  slice(1:12) |> mutate(n = 10) |>
  rename("mean_1" = mean, "sd_1" = sd, "n_1" = n) |> select(Week, mean_1, sd_1, n_1)


L17 = left_join(ms, control, by = "Week") |>
  mutate(article = "L2017") |> 
  mutate(mean_diff = mean_1 - mean_2,
         pooled_SD = sqrt(((n_1 - 1)*sd_1^2 + (n_2 - 1)*sd_2^2) / (n_1+n_2 - 2)),
         sd_diff = sd_1 - sd_2, 
         yij = mean_diff/pooled_SD) |> select(article, mean_diff, pooled_SD, yij, Week, sd_diff) |>
  mutate(timepoint = case_when(
    Week == "Intake W1" ~ 1,
    Week == "Intake W2" ~ 2,
    Week == "Intake W3" ~ 3, 
    Week == "Intake W4" ~ 4,
    Week == "Intake W5" ~ 5,
    Week == "Intake W6" ~ 6,
    Week == "Intake W7" ~ 7,
    Week == "Intake W8" ~ 8,
    Week == "Intake W9" ~ 9,
    Week == "Intake W10" ~ 10, 
    Week == "Intake W11" ~ 11,
    Week == "Intake W12" ~ 12,
    Week == "Intake W13" ~ 13,
    Week == "Intake W14" ~ 14
    
  )) |> select(-Week)

```


```{r}
full = full_join(full_join(full_join(full_join(full_join(full_join(L17, O11), P03), G07), GN06), D11), C15) |> select(-Phase) |> filter(timepoint <= 7)

mean.diff = full |> select(-pooled_SD, -yij) |> pivot_wider(names_from = timepoint, values_from = mean_diff) |> select(-article) 


```



























```{=tex}
\begin{align*}
y_{it} \sim N(\theta_{it}, \sigma^{2}_{it}) \quad \alpha_i \sim N(0, 100000) \\
\theta_{it} = \alpha_i + \beta_{i} \cdot time_{it} \quad \mu \sim N(0, 100000) \\
\beta_{i} \sim N(\mu, \tau^2) \quad \tau \sim N(0, 100), \: \tau >0
\end{align*}
```



$y_{it} =$ observed effect at time-point t in study i  
$\sigma^2_{it} =$ is the variance of $y_{it}$  
$\theta_{it} =$ is the true effect at time point t in study i  
$\alpha_i \: and \: \beta_i =$ respectively, the intercept and slope for the study-specific linear regression slope   
$time_{it} =$ the time-point in study i at time t  
$\mu =$ overall trend  
$\tau^2 =$ is the variance in trend between studies  



Comasco et al., 2015: weeks 1-5 (increasing)   
Daoura et al., 2011: weeks 1-5 (not increasing)  
Gustafsson et al., 2007: days 1-18, 19-36, 37-54 (not increasing)   
Lundberg et al., 2017: weeks 1-20 (increasing)  
Oreland et al., 2011: week 3-7 (increasing)  
Ploj et al., 2003: days 4, 4, 7, 11 (not increasing)  
Gustafsson & Nylander, 2006: days 1-18, 19-36, 37-54 (not increasing)    

# Analaysis 1: 

## Table 1: Groupings for Analysis 1  

```{=latex}
{\tiny
\centering
\begin{tabular}{lllllllll}
\hline
Article & Time-Point 1 & Time-Point 2 & Time-Point 3 & Time-Point 4 & Time-Point 5 & Time-Point 6 & Time-Point 7 \\
\hline
Comasco et al., 2015 & week 1 & week 2 & week 3 & week 4 & week 5 & NA & NA \\
Daoura et al., 2011 & week 1 & week 2 & week 3 & week 4 & week 5 & NA & NA \\
Gustafsson et al., 2007 & NA & days 1-18 & NA & days 19-36 & NA & days 37-54 & NA\\
Lundberg et al., 2017 & week 1 & week 2 & week 3 & week 4 & week 5 & week 6 & week 7 \\
Oreland et al., 2011 & NA & NA & week 3 & week 4 & week 5 & week 6 & week 7 \\
Ploj et al., 2003 & 4 days & 4 days & 7 days & 11 days & NA & NA & NA \\
Gustafsson \& Nylander, 2006 & NA & days 1-18 & NA & days 19-36 & NA & days 37-54 & NA \\
\hline
\end{tabular}}
```

* This analysis groups together both sexes and increasing ethanonl percentage with those that are not increasing.  


time-points = {time-point 1, time-point 2, time-point 3, time-point 4, time-point 5, time-point 6, time-point 7}   
study i = {C2015, D2011, G2007, L2017, O2011, P2003, GN2006}  

# Fitting Model With JAGS  


```{r}
library(rjags)
library(runjags)
library(R2jags)
library(lattice)
library(mcmcplots)
library(strex)
library(loo)
```

jagsOut1 = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary))))

loglik = jagsOut1 |> slice(40:72) |> summarise(loglik = sum(mean))
loglik

# AIC
(2*3 - 2*loglik$loglik)

# BIC
(-2*loglik$loglik + 4*log(32))



```{r model 1: basic}
# data
N = 7
t = c(6, 5, 4, 3, 3, 5, 6)
nChains = 4
burnInSteps = 1000
thinSteps = 50
numSavedSteps = 5000
nIter = ceiling((numSavedSteps * thinSteps)/nChains)
mean.diff = full |> mutate(timepoint = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  select(-pooled_SD, -yij, -sd_diff) |> pivot_wider(names_from = timepoint, values_from = mean_diff) |> select(-article) 
mean.diff = as.matrix(mean.diff)
mean.diff[is.na(mean.diff)] <- 0


sd_diff = full |> mutate(timepoint = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  select(-mean_diff, -yij, -pooled_SD) |> pivot_wider(names_from = timepoint, values_from = sd_diff) |> select(-article)


sd_diff = cbind(sd_diff)
sd_diff = as.matrix(sd_diff)
sd_diff[ is.na( sd_diff ) ] <- 0



time_period = full |> 
  select(-pooled_SD, -yij, -mean_diff, -sd_diff) |>
  mutate(timeperiod = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  pivot_wider(names_from = timeperiod, values_from = timepoint) |> select(-article) 
time_period = as.matrix(time_period)
time_period[is.na(time_period)] <- 0



params2 = c("beta", "tau", "theta")

----------------------
# prior: tau <- 1/vari
    ## vari <- pow(sd, 2)
    ## sd ~ dnorm(0, 0.01)I(0,)
modelstring = "
  model {
      for(i in 1:N) {
          for(j in 1:t[i]) {
              mean.diff[i, j] ~ dnorm(theta[i, j], prec[i, j])
              prec[i, j] <- 1/(sd_diff[i, j]* sd_diff[i, j])
              theta[i, j] <- beta[i]*time_period[i, j]
              loglik[i, j] <- logdensity.norm(mean.diff[i, j], theta[i, j], prec[i, j])
              }
          beta[i] ~ dnorm(beta.p, tau)  
      }
    beta.p ~ dnorm(0, 0.00001)
    tau <- 1/vari
    vari <- pow(sd, 2)
    sd ~ dnorm(0, 0.01)I(0,)
    pr.gr.zero <- step(beta.p) - equals(0, beta.p)
    }"
# writes to file: 
writeLines(modelstring, con="model1.txt")

jags = jags(model.file = 'model1.txt', data = list('t' = t, 'N' = N, 'mean.diff' = mean.diff, 'sd_diff' = sd_diff, 'time_period' = time_period), parameters.to.save =  c("beta", "tau", "theta", "loglik"), n.chains = nChains, n.iter = nIter, n.burnin = burnInSteps, n.thin = thinSteps)
print(jags)
plot(jags)
#denplot(jags.fit.mcmc, parms = c("theta"))
#denplot(jags.fit.mcmc, parms = c("beta"))
#denplot(jags.fit.mcmc, parms = c("tau"))
#traplot(jags.fit.mcmc, parms = c("theta"))


jagsOut1 = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary))))

loglik = jagsOut1 |> slice(40:72) |> summarise(loglik = sum(mean))
loglik

# AIC
(2*3 - 2*loglik$loglik)

# BIC
(-2*loglik$loglik + 4*log(32))



beta = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> slice(1:7) |> mutate(timepoint = c(1:7))
  
theta = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> slice(9:40) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))


for (i in 1:32) {
  w_i1 = (theta$sd)^2
  y_i1 = theta$mean
  mu_f1 = (sum(w_i1*y_i1)/sum(w_i1))
  
  Q[i] = sum(w_i1[i]* (y_i1[i]-mu_f1)^2 )
  Q1 = sum(Q[i])
}


w_i1 = theta$sd
w_i1 = w_i1^2
y_i1 = theta$mean
mu_f1 = (sum(w_i1*y_i1)/sum(w_i1))
Q1 = sum(w_i1*(y_i1-mu_f1)^2)

H1 = Q1/6
H1^2 # 0.009770292
I1 = (H^2-1)/H^2
I1^2

theta |> ggplot(aes(x = timepoint, y = mean, group = increasing)) +
  geom_point(aes(x = timepoint, y = mean, col = increasing, group = increasing)) +
  geom_smooth(aes(group = increasing, col = increasing, fill = increasing)) +
  labs(y = "Mean theta") +
  #geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article), alpha = 0.3) +
  theme_minimal() 

----------------------

# prior = gamma(0.01, 0.01)
modelstring = "
  model {
      for(i in 1:N) {
          for(j in 1:t[i]) {
              mean.diff[i, j] ~ dnorm(theta[i, j], prec[i, j])
              prec[i, j] <- 1/(sd_diff[i, j]* sd_diff[i, j])
              theta[i, j] <- beta[i]*time_period[i, j]
              }
          beta[i] ~ dnorm(beta.p, tau)        
      }
    beta.p ~ dnorm(0, 0.00001)
    tau <- 1/vari
    vari <- pow(sd, 2)
    sd ~ dgamma(0.01, 0.01)
    pr.gr.zero <- step(beta.p) - equals(0, beta.p)
    }"
# writes to file: 
writeLines(modelstring, con="model2.txt")

jags2 = jags(model.file = 'model2.txt', data = list('t' = t, 'N' = N, 'mean.diff' = mean.diff, 'sd_diff' = sd_diff, 'time_period' = time_period), parameters.to.save = params2, n.chains = nChains, n.iter = nIter, n.burnin = burnInSteps, n.thin = thinSteps)
print(jags2)
beta = tibble(as.data.frame(as.matrix(as.mcmc(jags2$summary)))) |> slice(1:7) |> mutate(timepoint = c(1:7))
  
theta = tibble(as.data.frame(as.matrix(as.mcmc(jags2$summary)))) |> slice(9:40) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))

w_i2 = theta$sd
y_i2 = theta$mean
mu_f2 = (sum(w_i*y_i)/sum(w_i))
Q2 = sum(w_i*(y_i-mu_f)^2)

H2 = Q/6
H2^2 # 0.009770292
I2 = (H^2-1)/H^2
I2^2

theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  #geom_line(aes(group = article))+
  geom_jitter()

theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  geom_smooth(aes(group = article), method = "lm", se = FALSE)+
  geom_point() +
  facet_wrap(~increasing)

theta |> ggplot(aes(x = timepoint, y = mean, group= timepoint)) +
  geom_line(aes(group = article, col = increasing)) +
  #geom_smooth(aes(group = article, col = increasing), method = "lm", se = FALSE)+
  geom_point() +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article, fill = increasing), alpha = 0.3)
  
beta |> ggplot(aes(x = timepoint, y = mean)) + 
  geom_line() + 
  geom_point() + 
   geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd), alpha = 0.3)


------------
# prior = sd ~ dgamma(0.1, 0.1)
modelstring = "
  model {
      for(i in 1:N) {
          for(j in 1:t[i]) {
              mean.diff[i, j] ~ dnorm(theta[i, j], prec[i, j])
              prec[i, j] <- 1/(sd_diff[i, j]* sd_diff[i, j])
              theta[i, j] <- beta[i]*time_period[i, j]
              }
          beta[i] ~ dnorm(beta.p, tau)        
      }
    beta.p ~ dnorm(0, 0.00001)
    tau <- 1/vari
    vari <- pow(sd, 2)
    sd ~ dgamma(0.1, 0.1)
    pr.gr.zero <- step(beta.p) - equals(0, beta.p)
    }"
# writes to file: 
writeLines(modelstring, con="model3.txt")

jags3 = jags(model.file = 'model3.txt', data = list('t' = t, 'N' = N, 'mean.diff' = mean.diff, 'sd_diff' = sd_diff, 'time_period' = time_period), parameters.to.save = params2, n.chains = nChains, n.iter = nIter, n.burnin = burnInSteps, n.thin = thinSteps)
print(jags3)

beta = tibble(as.data.frame(as.matrix(as.mcmc(jags3$summary)))) |> slice(1:7) |> mutate(timepoint = c(1:7))
  
theta = tibble(as.data.frame(as.matrix(as.mcmc(jags3$summary)))) |> slice(9:40) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))

w_i3 = theta$sd
y_i3 = theta$mean
mu_f3 = (sum(w_i3*y_i3)/sum(w_i3))
Q3 = sum(w_i3*(y_i3-mu_f3)^2)

H3 = Q3/6
H3^2 # 0.009739773
I3 = (H^2-1)/H^2
I3^2

theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  #geom_line(aes(group = article))+
  geom_point()

theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  geom_smooth(aes(group = article), method = "lm", se = FALSE)+
  geom_point() +
  facet_wrap(~increasing)

theta |> ggplot(aes(x = timepoint, y = mean, group= timepoint)) +
  geom_line(aes(group = article, col = increasing)) +
  #geom_smooth(aes(group = article, col = increasing), method = "lm", se = FALSE)+
  geom_point() +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article), alpha = 0.3)
  
beta |> ggplot(aes(x = timepoint, y = mean)) + 
  geom_line() + 
  geom_point() + 
   geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd), alpha = 0.3)



----------
# prior = sd ~ dnorm(0, 0.0000001)I(0,)
modelstring = "
  model {
      for(i in 1:N) {
          for(j in 1:t[i]) {
              mean.diff[i, j] ~ dnorm(theta[i, j], prec[i, j])
              prec[i, j] <- 1/(sd_diff[i, j]* sd_diff[i, j])
              theta[i, j] <- beta[i]*time_period[i, j]
              }
          beta[i] ~ dnorm(beta.p, tau)        
      }
    beta.p ~ dnorm(0, 0.0000001)
    tau <- 1/vari
    vari <- pow(sd, 2)
    sd ~ dnorm(0, 0.00001)I(0,)
    pr.gr.zero <- step(beta.p) - equals(0, beta.p)
    }"
# writes to file: 
writeLines(modelstring, con="model4.txt")

jags4 = jags(model.file = 'model4.txt', data = list('t' = t, 'N' = N, 'mean.diff' = mean.diff, 'sd_diff' = sd_diff, 'time_period' = time_period), parameters.to.save = params2, n.chains = nChains, n.iter = nIter, n.burnin = burnInSteps, n.thin = thinSteps)
print(jags4)



```


```{r}
H1^2
H2^2
H3^2

I1^2
I2^2
I3^2

print(jags$DIC)
print(jags2$DIC)
print(jags3$DIC)

print(jags$pD)
print(jags2$pD)
print(jags3$pD)

```







```{r heterogeneity in basic model 1...}
w_i = theta$sd
y_i = theta$mean
mu_f = (sum(w_i*y_i)/sum(w_i))
Q = sum(w_i*(y_i-mu_f)^2)

H = Q/6
H^2
I = (H^2-1)/H^2
I^2
```


```{r}
full |> ggplot(aes(x = mean_diff)) + geom_density()
full |> ggplot(aes(x = mean_diff, col = article)) + geom_density()
full |> ggplot(aes(x = timepoint, y = mean_diff)) + 
  geom_point() + 
  geom_line(aes(group = article))
full |> ggplot(aes(x = timepoint, y = mean_diff)) + 
  geom_point() + 
  geom_smooth(aes(group = article), method = "lm", se = FALSE)
```





































```{r model 1: theta estimates }

jag1 = jags.samples(jags$model, c("beta", "theta", "loglik"), nIter)
jag1$beta
jags1 = tibble(as.data.frame(as.matrix(as.mcmc(jags$BUGSoutput))))



jagsOut = tibble(as.data.frame(as.matrix(jags.fit.mcmc)))
one = jagsOut |> pivot_longer(c(1:58), names_to = "stat", values_to = "estimate")

jagsOut |> select(c(9:57)) |> slice(1) |> pivot_longer(c(1:49), names_to = "stat", values_to = "estimate") |> filter(estimate != 0) 

jagsOut.theta = jagsOut |> 
  pivot_longer(c(1:58), names_to = "stat", values_to = "theta.estimate") |> 
  slice(10:58) |> 
  filter(theta.estimate != 0) |>
  mutate(article = str_elem(stat, 7)) |>
  mutate(timepoint = str_elem(stat, 9)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))

# confidence interval for graph
jagsOut3.sd = 
  tibble(as.data.frame(as.matrix(as.mcmc(jags3$summary)))) |> 
  slice(1:32) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |>
  filter(mean != 0) |>
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |>
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))


jagsOut3.sd = jagsOut3.sd |> select('2.5%', '97.5%', article, timepoint) |> rename("2.5" = '2.5%',
                                                                                   "97.5" = '97.5%')

  
graph1 = left_join(jagsOut.theta, jagsOut3.sd) 
graph1 = left_join(graph1, theta)


graph1 |> ggplot(aes(x = timepoint, col = increasing, group = article)) +
  geom_point(aes(x = timepoint, y = theta.estimate)) +
  geom_line(aes(group = article, y = theta.estimate)) +
  theme_minimal() +
  scale_color_manual(values = c("pink", "purple")) +
  geom_hline(yintercept = 0)


meandiff |> ggplot(aes(x = timepoint, group = article)) +
  geom_point(aes(x = timepoint, y = mean, color = increasing)) +
  geom_line(aes(group = article, y = mean, color = increasing)) +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article, fill = increasing), alpha = 0.3) + # doesn't appear to be doing anything...
  theme_minimal() +
  scale_color_manual(values = c("pink", "purple")) +
  scale_fill_manual(values = c("pink", "purple")) +
  facet_wrap(~article) +
  geom_hline(yintercept = 0)


graph1 |> ggplot(aes(x = timepoint, group = article)) +
  geom_point(aes(x = timepoint, y = theta.estimate, col = increasing)) +
  geom_line(aes(group = article, y = theta.estimate, col = increasing)) +
  geom_ribbon(aes(ymin = theta.estimate - sd, ymax = theta.estimate + sd, group = article, fill = increasing), alpha = 0.3) +
  theme_minimal() +
  scale_color_manual(values = c("pink", "purple")) +
  scale_fill_manual(values = c("pink", "purple")) +
  facet_wrap(~increasing) +
  geom_hline(yintercept = 0)

graph1 |> ggplot(aes(x = timepoint, group = article)) +
  geom_point(aes(x = timepoint, y = theta.estimate, col = increasing)) +
  geom_line(aes(group = article, y = theta.estimate, col = increasing)) +
  geom_ribbon(aes(ymin = theta.estimate - sd, ymax = theta.estimate + sd, group = article, fill = increasing), alpha = 0.3) +
  theme_minimal() +
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_wrap(~increasing) +
  geom_hline(yintercept = 0)
  
```



```{r model 1: mean beta}
jagsOut.beta = 
  tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> 
  slice(1:7) |>
  mutate(stat = c("beta[1]", "beta[2]", "beta[3]", "beta[4]", "beta[5]", "beta[6]", "beta[7]")) |>
  filter(mean != 0) |>
  mutate(group = 1) |>
  mutate(timepoint = str_elem(stat, 6)) 
  
jagsOut.beta |> ggplot(aes(x = timepoint, y = mean)) +
  geom_point(aes(x = timepoint, y = mean)) +
  geom_line(aes(group = group)) +
  labs(y = "Mean Beta") +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = group), alpha = 0.3) +
  theme_minimal() 


```




```{r}
beta = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> slice(1:7) |> mutate(timepoint = c(1:7))
  
theta = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> slice(9:40) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))
meandiff = tibble(as.data.frame(as.matrix(as.mcmc(jags$summary)))) |> 
  slice(41:72) |> 
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))


theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  #geom_line(aes(group = article))+
  geom_point()

theta |> ggplot(aes(x = timepoint, y = mean, col = increasing, group= timepoint)) +
  geom_boxplot() +
  geom_smooth(aes(group = article), method = "lm", se = FALSE)+
  geom_point() +
  facet_wrap(~increasing)

theta |> ggplot(aes(x = timepoint, y = mean, group= timepoint)) +
  geom_line(aes(group = article, col = increasing)) +
  #geom_smooth(aes(group = article, col = increasing), method = "lm", se = FALSE)+
  geom_point() +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article), alpha = 0.3)+
  facet_wrap(~increasing)
  
beta |> ggplot(aes(x = timepoint, y = mean)) + 
  geom_line() + 
  geom_point() + 
   geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd), alpha = 0.3)

```






```{r model 2: adding predictor variable to account for}
# data
N = 7
t = c(6, 5, 4, 3, 3, 5, 6)
mean.diff = full |> 
  select(-pooled_SD, -yij) |> 
  mutate(timepoint = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  pivot_wider(names_from = timepoint, values_from = mean_diff) |> 
  select(-article) 
mean.diff = as.matrix(mean.diff)
mean.diff[is.na(mean.diff)] <- 0

sd_diff = full |> 
  select(-mean_diff, -yij) |> 
  mutate(timepoint = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  pivot_wider(names_from = timepoint, values_from = pooled_SD) |> 
  select(-article) 
sd_diff = cbind(sd_diff)
sd_diff = as.matrix(sd_diff)
sd_diff[ is.na( sd_diff ) ] <- 0

time_period = full |> 
  select(-pooled_SD, -yij, -mean_diff) |> 
  mutate(timepoint = c(1, 2, 3, 4, 5, 6, 
                             1, 2, 3, 4, 5, 
                             1, 2, 3, 4, 
                             1, 2, 3,
                             1, 2, 3,
                             1, 2, 3, 4, 5,
                             1, 2, 3, 4, 5, 6)) |>
  pivot_wider(names_from = timepoint, values_from = timepoint) |> 
  select(-article) 
time_period = as.matrix(time_period)
time_period[is.na(time_period)] <- 0


increasing = c(0, 1, 1, 0, 0, 0, 1)


params2 = c("beta", "tau", "theta", "mean.diff")

params = c("beta")

modelstring = "
  model {
      for(i in 1:N) {
          for(j in 1:t[i]) {
              mean.diff[i, j] ~ dnorm(theta[i, j], prec[i, j])
              prec[i, j] <- 1/(sd_diff[i, j]* sd_diff[i, j])
              theta[i, j] <- beta[i]*time_period[i, j]+beta[i]*increasing[i]
              }
          beta[i] ~ dnorm(beta.p, tau)        
      }
    beta.p ~ dnorm(0, 0.00001)
    tau <- 1/vari
    vari <- pow(sd, 2)
    sd ~ dnorm(0, 0.01)I(0,)
    pr.gr.zero <- step(beta.p) - equals(0, beta.p)
    }"
# writes to file: 
writeLines(modelstring, con="model11.txt")



jagsmod2 = jags(model.file = 'model11.txt', data = list('t' = t, 'N' = N, 'mean.diff' = mean.diff, 'sd_diff' = sd_diff, 'time_period' = time_period, 'increasing' = increasing), parameters.to.save = c("beta", "theta"),n.chains = nChains, n.iter = nIter, n.burnin = burnInSteps, n.thin = thinSteps)
print(jagsmod2)



#jagsOut = tibble(as.data.frame(as.matrix(jagsmod2.fit.mcmc)))
jagsOutm2 = tibble(as.data.frame(as.matrix(jagsmod2$summary)))

betam2 = jagsOutm2 |> slice(1:7) |> mutate(stat = c("beta[1]", "beta[2]", "beta[3]", "beta[4]", "beta[5]", "beta[6]", "beta[7]")) |>
  filter(mean != 0) |>
  mutate(group = 1) |>
  mutate(timepoint = str_elem(stat, 6)) 

betam2 |> ggplot(aes(x = timepoint, y = mean)) +
  geom_point(aes(x = timepoint, y = mean)) +
  geom_line(aes(group = group)) +
  labs(y = "Mean Beta") +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = group), alpha = 0.3) +
  theme_minimal() 



thetam2 = jagsOutm2 |> slice(8:39) |>
  mutate(stat = c("mean.diff[1,1]", "mean.diff[3,1]", "mean.diff[6,1]", "mean.diff[7,1]", "mean.diff[1,2]", "mean.diff[3,2]", "mean.diff[4,2]", "mean.diff[5,2]", "mean.diff[6,2]", "mean.diff[7,2]", "mean.diff[1,3]", "mean.diff[2,3]", "mean.diff[3,3]", "mean.diff[6,3]", "mean.diff[7,3]", "mean.diff[1,4]", "mean.diff[2,4]", "mean.diff[3,4]", "mean.diff[4,4]", "mean.diff[5,4]", "mean.diff[6,4]", "mean.diff[7,4]", "mean.diff[1,5]", "mean.diff[2,5]",
"mean.diff[6,5]", "mean.diff[7,5]", "mean.diff[1,6]", "mean.diff[2,6]", "mean.diff[4,6]", "mean.diff[5,6]", "mean.diff[7,6]", "mean.diff[2,7]")) |> 
  mutate(article = str_elem(stat, 11)) |>
  mutate(timepoint = str_elem(stat, 13)) |> 
  select(-stat) |> 
  mutate(increasing = case_when(
  article == 1 ~ "Steady",
  article == 2 ~ "Increasing",
  article == 3 ~ "Increasing", 
  article == 4 ~ "Steady",
  article == 5 ~ "Steady", 
  article == 6 ~ "Steady",
  article == 7 ~ "Increasing"
))

thetam2 |> ggplot(aes(x = timepoint, y = mean)) +
  geom_point(aes(x = timepoint, y = mean, col = increasing)) +
  geom_line(aes(group = article, col = increasing)) +
  labs(y = "Mean theta") +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, group = article), alpha = 0.3) +
  theme_minimal() +
  facet_wrap(~article)



meandiffm2 = jagsOutm2 |> slice(41:79)

```
















